My title

### 2024-09-21 paper/paper.qmd
did some comment & cleaning of files + updated reference page + added a table counting the different types of sessions

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Wendy Yuan
thanks: "Code and data are available at: LINK."
date: "27 September 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

cleaned_data <- read_csv(here::here("data/cleaned_data/cleaned_data.csv"))
```

@@

@@

ggplot(cleaned_data, aes(x = session_type, fill = present)) +
  geom_bar(position = "dodge2") 
```

@@

cleaned_data |> 
  ggplot(aes(x = session_month, fill = present)) +
  geom_bar(position = "dodge2") 
```

```{r}
#| label: fig-session_year
#| fig-cap: Comparison of Attendance between 2022 & 2024
#| echo: false

cleaned_data |> 
  ggplot(aes(x = session_year, fill = present)) +
  geom_bar(position = "dodge2") 
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Wendy Yuan
date: "27 September 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

cleaned_data <- read_csv(here::here("data/cleaned_data/cleaned_data.csv"))
```
\newpage

@@

```{r}
#| label: fig-count
#| fig-cap: Count of Number of Sessions per Year, Month, & Type
#| echo: false

table(cleaned_data$session_type)

cleaned_data$session_month <- factor(cleaned_data$session_month, levels = month.abb)
table(cleaned_data$session_month)

table(cleaned_data$session_year)
```

@@

ggplot(cleaned_data, aes(x = session_type, fill = present)) +
  geom_bar(position = "dodge2") + 
  labs(
    title = "Present vs Absence in Different Session Types",
    x = "Session Type",
    y = "Count"
  )
```

@@

cleaned_data |> 
  ggplot(aes(x = session_month, fill = present)) +
  geom_bar(position = "dodge2") + 
  labs(
    title = "Present vs Absence Over Different Months",
    x = "Months",
    y = "Count"
  )
```

```{r}
#| label: fig-session_year
#| fig-cap: Comparison of Attendance between 2022 to 2024
#| echo: false

cleaned_data |> 
  ggplot(aes(x = session_year, fill = present)) +
  geom_bar(position = "dodge") + 
  labs(
    title = "Present vs Absence Over Different Years",
    x = "Years",
    y = "Count"
  )
```
